---

---


# Time-based Metrics



```{r bedside_stemi, fig.height = 3, fig.path="figures/", eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

time_data <- filter(time_data, !is.na(time_data$mean_bedside_stemi)) %>%
        droplevels()

progs <- levels(as.factor(time_data$program_name)) 

for(i in progs) {
        
bedside_data <- 
        time_data %>%
        filter(!is.na(mean_bedside_stemi)) %>%
        filter(program_name == i)
        #filter(program_name == params$program_name)

qic(y = mean_bedside_stemi,
    x = month,
    data = bedside_data,
    chart = "run",
    main = paste0(i, 
                  "Average bedside time for STEMI activation patients"),
    ylab = "Avg minutes",
    xlab = ""
    
)

}


```

```{r scene_stemi, fig.cap="",  fig.path="figures/", eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

time_data <- 
        monthly_data %>%
        select(program_name, month, total_patients, mean_mobilization, stemi_cases,
               mean_bedside_stemi, mean_scene_stemi)

time_data <- filter(time_data, !is.na(time_data$mean_scene_stemi)) %>%
        droplevels()

progs <- levels(as.factor(time_data$program_name)) 

for(i in progs) {
        
scene_data <- 
        time_data %>%
        filter(!is.na(mean_scene_stemi)) %>%
        filter(program_name == i)
        #filter(program_name == params$program_name)

qic(y = mean_scene_stemi,
    x = month,
    data = scene_data,
    chart = "run",
    main = paste0(i, "Average scene time for STEMI activation patients"),
    ylab = "Avg minutes",
    xlab = ""
    
)



}

```

```{r mobilization, fig.height = 3, fig.cap="",  fig.path="figures/", eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

mobilization_data <- 
        time_data %>%
        filter(!is.na(mean_mobilization)) %>%
        droplevels() %>%
        #filter(program_name == i)
        filter(program_name == program)
        
```

## Mobilization Times  

`r if(nrow(mobilization_data) < 6) {'_insufficient data_'} else {' '}`

```{r mobilization runchart, fig.height = 3}


## build chart if at least 6 data points
if(nrow(mobilization_data) >= 6) {
        
        
qic(y = mean_mobilization,
    x = month,
    data = mobilization_data,
    chart = "run",
    main = paste0("Average Mobilization Time of the transport team" ),
    ylab = "Avg minutes",
    xlab = ""
    
)

    show_timeData("TM-1", program)

}


```


```{r stemi bedside, fig.height = 3, fig.cap="",  fig.path="figures/", eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

stemi_bedside_data <- 
        time_data %>%
        filter(!is.na(mean_bedside_stemi)) %>%
        droplevels() %>%
        #filter(program_name == i)
        filter(program_name == program)
        
```

## STEMI Bedside Times  

`r if(nrow(stemi_bedside_data) < 6) '_insufficient data_'`

```{r stemi bedside runchart, fig.height = 3}


## build chart if at least 6 data points
if(nrow(stemi_bedside_data) >= 6) {
        
        
qic(y = mean_bedside_stemi,
    x = month,
    data = stemi_bedside_data,
    chart = "run",
    main = paste0("Average STEMI Bedside Time of the transport team" ),
    ylab = "Avg minutes",
    xlab = ""
    
)
show_timeData("TM-2a", program)

}



```

```{r stemi scene, fig.height = 3, fig.cap="",  fig.path="figures/", eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

stemi_scene_data <- 
        time_data %>%
        filter(!is.na(mean_scene_stemi)) %>%
        droplevels() %>%
        #filter(program_name == i)
        filter(program_name == program)
        
```

## STEMI Scene Times  

`r if(nrow(stemi_scene_data) < 6) '_insufficient data_'`

```{r stemi scene runchart, fig.height = 3}


## build chart if at least 6 data points
if(nrow(stemi_scene_data) >= 6) {
        
        
qic(y = mean_scene_stemi,
    x = month,
    data = stemi_scene_data,
    chart = "run",
    main = paste0("Average STEMI Scene Time of the transport team" ),
    ylab = "Avg minutes",
    xlab = ""
    
)
show_timeData("TM-2b", program)

}



```



