---
title: "GAMUT Update"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    fig_height: 8
    toc_depth: 1
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(dev = 'pdf')
options(scipen = 4)

## change group to "ID" to use anonymized ID
group <- "program_name" 
#group <- "ID"

```


```{r load_data, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr) 
library(dplyr)
library(GAMUT)
library(zoo)

#GAMUT_data("data/GAMUT.Rdata")

load("data/GAMUT.Rdata")

#metricData$mark <- 19
#metricData$mark <- ifelse(substr(metricData$program_name, 1, 3) %in% c("AEL", "AIM"), 
# 6,20)

```
<!-- Intro -->
# Introduction


```{r overview, echo=FALSE}
reporting <- table(monthly_data$program_name)
total.enrolled <- length(reporting)
total.not_reporting <- length(reporting[reporting == 0])
total.reporting <- length(reporting[reporting > 0])
total.partial <- length(reporting[reporting > 0 & reporting <= 3])
total.full <- length(reporting[reporting >=10])


```  

As of `r GAMUT_date_loaded`, there are  `r total.enrolled` total programs enrolled with  `r total.reporting` reporting data and `r total.full` reporting at least 10 consecutive months. 

This accounts for `r sum(monthly_data$total_patients)` total patient encounters (`r sum(monthly_data$total_neo_patients, na.rm=TRUE)` neonatal, `r sum(monthly_data$total_peds_patients, na.rm=TRUE)` pediatric, and `r sum(monthly_data$total_adult_patients, na.rm=TRUE)` adult encounters).
 
```{r hist_reporting, fig.path="figures/", fig.height=3.5, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
hist(reporting, 
     main="",
     xlab="number of months reported", 
     breaks=12)

```
\newpage

```{r program_list}

```



\newpage  

<!-- End Intro --> 


# Overall Advanced Airway Management

<!-- Overall Advance Airway Management -->
## Mechanical Ventilation - All Patients
```{r vent_adv_airway, fig.path="figures/", fig.height=9, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="adv_airway_ventilator", 
               den="adv_airway_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with 
    an advanced airway supported by a mechanical ventilator",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = 16
                             )
metric.table$plot
```

## Waveform Capnography - All Patients
```{r waveform_capno, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="adv_airway_wave_capno", 
               den="adv_airway_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with advanced airways
 in whom continuous waveform capnography was used.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Confirmed tracheal tube placement - All Patients
```{r confirmed_tt, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="adv_airway_tt_confirmed", 
               den="adv_airway_tt_cases"
               )

metric.table <- plot_metrics(
    "Percent of intubated patient transport contacts 
with documentation of confirmed tracheal tube placement.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## RSI protocol compliance - All Patients
```{r RSI_compliance, include=TRUE,  fig.path="figures/", fig.height=6, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_rsi_compliant", 
               den="intub_rsi_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts undergoing RSI 
where all indicated elements of the program’s RSI protocol were completed.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

<!-- End Overall Advanced Airway Management -->



<!-- Neonatal Adv Airway Management -->
# Neonatal Advanced Airway Management 
## Neonatal - Mechanical Ventilation
```{r neo_vent_adv_airway, fig.path="figures/", include=TRUE, fig.height=6, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="neo_adv_airway_vent", 
               den="neo_adv_airway_cases"
               )

metric.table <- plot_metrics(
    "Percent of Neonatal patient transport contacts with 
    an advanced airway supported by a mechanical ventilator",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Neonatal - Waveform Capnography
```{r neo_waveform_capno, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="neo_adv_airway_capno", 
               den="neo_adv_airway_cases"
               )

metric.table <- plot_metrics(
    "Percent of Neonatal patient transport contacts with advanced airways
 in whom continuous waveform capnography was used.",
    program_name = plotData$group,
    num = plotData$num,
    den = plotData$den,
    reordering = "increasing", 
    pch = plotData$mark
)
metric.table$plot
```

## Neonatal - First Attempt Success
```{r first_attempt_success_neo,  eval=FALSE, fig.path="figures/", include=TRUE, fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_neo_first_success", 
               den="intub_neo_attempts"
               )

metric.table <- plot_metrics(
    "Neonatal - Percent of patient transport contacts successfully intubated 
    on the 1st attempt by the transport team",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot

```

## Neonatal - DASH-1A
```{r DASH1A_neo, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_neo_no_hypoxia", 
               den="intub_neo_attempts"
               )

metric.table <- plot_metrics(
    "Neonatal - Percent of patients with definitive airway during the 1st attempt 
    by the transport team without suffering hypoxia or hypotension",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```
<!-- End Neonatal Adv Airway Management -->


<!-- Pediatric Adv Airway Management -->
# Pediatric Advanced Airway Management
## Pediatric - Mechanical Ventilation
```{r ped_vent_adv_airway, fig.path="figures/", include=TRUE, fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="ped_adv_airway_vent", 
               den="ped_adv_airway_cases"
               )

metric.table <- plot_metrics(
    "Percent of Pediatric patient transport contacts with 
    an advanced airway supported by a mechanical ventilator",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Pediatric - Waveform Capnography
```{r ped_waveform_capno, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

metric.table <- plot_metrics(
    "Percent of Pediatric patient transport contacts with advanced airways
 in whom continuous waveform capnography was used.",
    program_name = plotData$group,
    num = plotData$num,
    den = plotData$den,
    reordering = "increasing", 
    pch = plotData$mark
)
metric.table$plot
```

## Pediatric - First Attempt Success
```{r first_attempt_success_ped, eval=FALSE, fig.path="figures/", include=TRUE, fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_ped_first_success", 
               den="intub_ped_attempts"
               )

metric.table <- plot_metrics(
    "Pediatric - Percent of patient transport contacts successfully intubated 
    on the 1st attempt by the transport team",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Pediatric - DASH-1A 
```{r DASH1A_ped, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_ped_no_hypoxia", 
               den="intub_ped_attempts"
               )

metric.table <- plot_metrics(
    "Pediatric - Percent of patients with definitive airway during the 1st attempt 
    by the transport team without suffering hypoxia or hypotension",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot

```

<!-- End Pediatric Adv Airway Management -->


<!-- Adult Adv Airway Management -->
# Adult Advanced Airway Management  
## Adult - Mechanical Ventilation
```{r adult_vent_adv_airway, fig.path="figures/", include=TRUE, fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="adult_adv_airway_vent", 
               den="adult_adv_airway_cases"
               )
#plotData <- plotData[plotData$den >= 50,]


metric.table <- plot_metrics(
    "Percent of Adult patient transport contacts with 
    an advanced airway supported by a mechanical ventilator",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Adult - Waveform Capnography
```{r adult_waveform_capno, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="adult_adv_airway_capno", 
               den="adult_adv_airway_cases"
               )

#plotData <- plotData[plotData$den >= 50,]

metric.table <- plot_metrics(
    "Percent of Adult patient transport contacts with advanced airways
 in whom continuous waveform capnography was used.",
    program_name = plotData$group,
    num = plotData$num,
    den = plotData$den,
    reordering = "increasing", 
    pch = plotData$mark
)
metric.table$plot
```

## Adult - First Attempt Success
```{r first_attempt_success_adult, eval=FALSE, fig.path="figures/",  fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_adult_first_success", 
               den="intub_adult_attempts"
               )

metric.table <- plot_metrics(
    "Adult - Percent of patient transport contacts successfully intubated 
    on the 1st attempt by the transport team",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Adult - DASH-1A
```{r DASH1A_adult, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="intub_adult_no_hypoxia", 
               den="intub_adult_attempts"
               )

metric.table <- plot_metrics(
    "Adult - Percent of patients with definitive airway during the 1st attempt 
    by the transport team without suffering hypoxia or hypotension",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

<!-- End Adult Adv Airway Management -->


<!-- General Metrics -->
# General Metrics
## Reliable pain assessments
```{r pain_assessment, include=TRUE,  fig.path="figures/", fig.height=6, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="pain_scale_used", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with a 
documented pain assessment.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```


## HEMS Over-triage
```{r hems_over_triage, include=TRUE,  fig.path="figures/", fig.height=4, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="hems_ed_discharge", 
               den="hems_cases"
               )

metric.table <- plot_metrics(
    "Percent of the HEMS patient transport contacts 
discharged without hospital admission",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```


```{r hems_over_triage_table, results='asis', include=TRUE,  fig.path="figures/", fig.height=4, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
cat("### Details")

HEMS <- 
    monthly_data %>%
    select(month, program_name, num=hems_ed_discharge, den=hems_cases) %>%
    filter(!is.na(num), 
           !is.na(den),
            den > 0, 
            den >= num) 

kable(HEMS)
```




## Cases involving CPR
```{r cpr, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="cpr_cases", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Rolling 12 month CPR rate per 10,000 transports",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000",
                             pch = plotData$mark
                             )
metric.table$plot
```


## Generalized Handoff tool
```{r handoff_tool, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="standardized_handoffs", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Percent of cases involving a standardized patient care hand-off",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```
<!-- End general metrics -->



\newpage  

<!-- Focused Populations -->

# Focused Populations  
## Neonatal Hypothermia on Arrival  
```{r neonatal_hypothermia, fig.cap="",  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="unintended_hypothermia", 
               den="total_neo_patients"
               )

metric.table <- plot_metrics("Percent of neonates found \nhypothermic upon admission",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

## Blood glucose check for altered mental status  
```{r bg_check, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="alt_ment_bg_checks", 
               den="alt_ment_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with altered mental status 
    or focal neurologic deficit with a documented blood glucose check.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing",
                             pch = plotData$mark
                             )
metric.table$plot
```

## STEMI Bedside
```{r bedside_stemi, fig.cap="",  fig.path="figures/", fig.height=4, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

bedside_overall <- mydata[mydata$mean_bedside_stemi > 0 & 
                            !is.na(mydata$mean_bedside_stemi) & 
                            !is.na(mydata$stemi_cases),c("mean_bedside_stemi", "stemi_cases")]

rate.overall <- weighted.mean(bedside_overall$mean_bedside_stemi, bedside_overall$stemi_cases)

metric.table <- plot_metrics_wm(
    "Average bedside time for 
STEMI activation patients",
                             program_name = bedside_stemi$group,
                             wavg = bedside_stemi$bedside_stemi.wavg,
                             rate_overall= rate.overall,
                             num = sum(bedside_overall$stemi_cases),
                             reordering="decreasing",
                             qlabel="Weighted average* time in minutes"
                             )

#metric.table$plot
```

## STEMI Scene
```{r scene_stemi, fig.cap="",  fig.path="figures/", fig.height=4, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}


scene_overall <- mydata[mydata$mean_scene_stemi > 0 & 
                            !is.na(mydata$mean_scene_stemi) & 
                            !is.na(mydata$stemi_cases),c("mean_scene_stemi", "stemi_cases")]

rate.overall <- weighted.mean(mydata$mean_scene_stemi, mydata$stemi_cases, na.rm=TRUE)


metric.table <- plot_metrics_wm(
    "Average scene time for 
STEMI activation patients",
                             program_name = scene_stemi$group,
                             wavg = scene_stemi$scene_stemi.wavg,
                             rate_overall= rate.overall,
                             num = sum(scene_overall$stemi_cases), 
                             reordering="decreasing",
                             qlabel="Weighted average* time in minutes"
                             )

#metric.table
```

## ECG interpretation for STEMI patients

```{r ecg_stemi, include=TRUE,  fig.path="figures/", fig.cap="Data only reported for one  month by 1 program", fig.height=4, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="ecg_accurate_interpret", 
               den="ecg_cases"
               )

metric.table <- plot_metrics(
    "Percent of transport patient contacts with accurately 
interpreted 12-lead ECG evaluations",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing"
                             )
metric.table$plot
```


```{r ecg_stemi_table, results='asis', include=TRUE,  fig.path="figures/", fig.height=4, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
cat("### Details")

STEMI <- 
    monthly_data %>%
    select(month, program_name, num=ecg_accurate_interpret, den=ecg_cases) %>%
    filter(!is.na(num), 
           !is.na(den),
            den > 0, 
            den >= num) 

kable(STEMI)
```

## Management of hypertension in hemorrhagic stroke
```{r htn_hem_stroke, include=TRUE,  fig.path="figures/", fig.height=6, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="hem_stroke_bp_managed", 
               den="hem_stroke_cases"
               )

metric.table <- plot_metrics(
    "Percent of transport patient contacts with 
hemorrhagic stroke and appropriate blood pressure management",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing",
                             pch = plotData$mark
                             )
metric.table$plot
```

\newpage  

## Appropriate management of hemorrhagic shock
```{r hem_shock_managed, include=TRUE,  fig.path="figures/", fig.height=2, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="hem_shock_managed", 
               den="hem_shock_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with 
hemorrhagic shock appropriately managed",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing",
                             pch = plotData$mark
                             )
metric.table$plot
```

\newpage  

## Appropriate management of blood pressure for aortic emergencies
```{r bp_aortic, include=TRUE,  fig.path="figures/", fig.height=6, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="aortic_dissect_managed", 
               den="aortic_dissect_cases"
               )

metric.table <- plot_metrics(
    "Percent of patient transport contacts with known or suspected 
    aortic dissection receiving indicated blood pressure and heart rate therapies.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "increasing", 
                             pch = plotData$mark
                             )
metric.table$plot
```

<!-- End focused populations --> 



<!-- Rare Events  -->

# Rare Events

## Patient Injuries
```{r patient_injuries, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="patient_injuries", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Patient injuries 
    per 10,000 patient transport contacts.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )
metric.table$plot
```


## Crew Injuries
```{r crew_injuries, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="crew_injuries", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Crew injuries 
    per 10,000 patient transport contacts.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )
metric.table$plot
```


## Medical equipment failure
```{r med_equip_failure, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="med_equip_failure", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Medical equipment failures 
    per 1000 patient transport contacts.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 1000",
                             qlabel = "Estimated cases per 1000"
                             )
metric.table$plot
```


## Unplanned device dislodgements
```{r device_dislogement, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="dislodgements", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Unplanned dislodgements of therapeutic devices 
    per 1000 patient transport contacts",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 1000",
                             qlabel = "Estimated cases per 1000"
                             )
metric.table$plot
```

## Medication errors on transport
```{r med_error, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="medication_errors", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "(Rolling 12 month) medication error rate 
    per 10,000 patient transport contacts.",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )
metric.table$plot
```


## Rate of Serious Reportable Event
```{r sre, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="sre", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "(Rolling 12 month) SRE rate 
    per 10,000 patient transport contacts",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )
metric.table$plot
```

## Patient near-miss events 
```{r nearmiss, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="near_miss", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "(Rolling 12 month) transport-related patient mishap rate 
    per 10,000 patient transport contacts",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )

metric.table$plot
```

## Adverse drug event during transport
```{r ade, include=TRUE,  fig.path="figures/", fig.height=9, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

plotData <- pd(group=group, 
               num="ade", 
               den="total_patients"
               )

metric.table <- plot_metrics(
    "Adverse drug events 
    per 10,000 patient transport contacts",
                             program_name = plotData$group,
                             num = plotData$num,
                             den = plotData$den,
                             reordering = "decreasing",
                             rate = "per 10000",
                             qlabel = "Estimated cases per 10000"
                             )

metric.table$plot

```


<!-- End Rare Events -->
