---
title: "Untitled"
author:
- Rollie Parrish
- <rollie.parrish@providence.org>
output:
  html_document: default
  geometry: margin=.75in
  fontsize: 11pt
  pdf_document:
    highlight: tango
    includes:
      in_header: header.tex
---


```{r initial_setup, echo=FALSE, message=FALSE, warning=FALSE}
library(RPamisc)
library(dplyr)
library(knitr)
library(lubridate)
library(zoo)

options(scipen = 10)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = "")

```

# Prompt

 - What is being requested? Purpose or use?
 - Population of interest - Inclusions & Exclusions
 - Intervention or comparision groups?
 - Outcomes/Variables?
 - Date Ranges? 

 
# Sources


```{r load_data}

#.hem_onc_sedation_raw <- tbl_df(edwSQL("../SQL/WSH Hem Onc Sedation.sql", resource="Trantor")$data)

```

# Methods


# Results


# References

---
references:
- id: fenner2012a
  title: One-click science marketing
  author:
  - family: Fenner
    given: Martin
  container-title: Nature Materials
  volume: 11
  URL: 'http://dx.doi.org/10.1038/nmat3283'
  DOI: 10.1038/nmat3283
  issue: 4
  publisher: Nature Publishing Group
  page: 261-263
  type: article-journal
  issued:
    year: 2012
    month: 3
---
