---
title: "GAMUT 2015 Summary Report"
author: ''
date: '`r paste(params$program_name)`'
output:
  html_document:
    toc: no
  fontsize: 11pt
  pdf_document:
    highlight: tango
    includes:
      in_header: header.tex
    toc: no
params:
  dag: Akron Childrens
  end_date: '2016-01-01'
  operator: ''
  program_name: Childrens Hospital Philadelphia
  start_date: '2015-01-01'
---


```{r initial_setup, echo=FALSE, message=FALSE, warning=FALSE}
library(REDCapR)
library(knitr)
library(plyr)
library(dplyr)
library(magrittr)
library(GAMUT)
library(zoo)
library(beeswarm)
library(qicharts)


options(scipen = 10)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = "")


```
```{r load_data}
# Uncomment next line to get new data from REDCap
#GAMUT_data("GAMUT.Rdata")
load("GAMUT.Rdata")

# Filter 
monthly_data <- filter(monthly_data,
                       month >= params$start_date & 
                       month < params$end_date)

dag <- params$dag
operator <- params$operator

```

\pagestyle{fancy}
\fancyheadoffset{0cm}
\rhead{}
\lhead{`r dag`}
\chead{GAMUT 2015 Summary Report}
\cfoot{Confidential report for quality improvement purposes}
\fancyfoot[LE,RO]{\thepage}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\thispagestyle{empty}
\begin{center}
%\Large{`r paste(dag, ifelse(operator == "AIM", "Air Methods", ""))`}
\vfill
`r paste("Report generated on ", Sys.Date())`

\end{center}  



\newpage  

# Time-based Metrics


```{r time data,  eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

time_data <- 
        monthly_data %>%
        select(program_name, month, total_patients, mean_mobilization, stemi_cases,
               mean_bedside_stemi, mean_scene_stemi)

```


## STEMI Times

```{r bedside_stemi, fig.path="figures/", eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}


main = "Average bedside time for STEMI activation patients"

```

```{r scene_stemi, fig.cap="",  fig.path="figures/", fig.height=10, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

main = "Average scene time for STEMI activation patients"

```

## Mobilization Times
```{r mobilization, fig.cap="",  fig.path="figures/", eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

time_data <- filter(time_data, !is.na(time_data$mean_mobilization)) %>%
        droplevels()

progs <- levels(as.factor(time_data$program_name)) 

for(i in progs) {
        
mobilization_data <- 
        time_data %>%
        filter(!is.na(mean_mobilization)) %>%
        filter(program_name == i)
        #filter(program_name == params$program_name)

qic(y = mean_mobilization,
    x = month,
    data = mobilization_data,
    chart = "run",
    main = paste0(i, 
                  ": Average Mobilization Time of the transport team" ),
    ylab = "Avg minutes",
    xlab = ""
    
)

}

```



